Using numerical modelling to investigate temperature and wave exposure as drivers

### 2020-11-21 thesis_chapter_2.Rmd
chapter 2 updates

library(tidyverse)
library(ggpubr)
library(gridExtra)
library(ggplot2)
library(ggord)
library(vegan)

@@

wp_1 <- rasterGrob(as.raster(readJPEG("figures/chapter_2/fig_6A.jpg")))
wp_2 <- rasterGrob(as.raster(readJPEG("figures/chapter_2/fig_6B.jpg")))
wp_3 <- rasterGrob(as.raster(readJPEG("figures/chapter_2/fig_6C.jpg")))
wp_4 <- rasterGrob(as.raster(readJPEG("figures/chapter_2/fig_6D.jpg")))
wp_5 <- rasterGrob(as.raster(readJPEG("figures/chapter_2/fig_6E.jpg")))
wp_6 <- rasterGrob(as.raster(readJPEG("figures/chapter_2/fig_6_legend.jpg")))

>>>>

library(tidyverse)
library(ggpubr)
library(gridExtra)
library(ggplot2)
#library(ggord)
library(vegan)

@@

wp_1 <- rasterGrob(as.raster(readJPEG("figures/chapter_2/fig_6A.jpg"))) #figure missing, copy of fig_6B used
wp_2 <- rasterGrob(as.raster(readJPEG("figures/chapter_2/fig_6B.jpg")))
wp_3 <- rasterGrob(as.raster(readJPEG("figures/chapter_2/fig_6C.jpg")))
wp_4 <- rasterGrob(as.raster(readJPEG("figures/chapter_2/fig_6D.jpg")))
wp_5 <- rasterGrob(as.raster(readJPEG("figures/chapter_2/fig_6E.jpg")))
wp_6 <- rasterGrob(as.raster(readJPEG("figures/chapter_2/fig_6_legend.jpg")))
